Vectorizing Python Constructs Using Pythran and Boost SIMD

### 2013-11-22 doc/papers/wpmvp14/paper.tex
Abstract!

\usepackage{amsmath}

@@

\begin{abstract}
This is the text of the abstract.
\end{abstract}

@@

>>>>

\usepackage{amsmath}
\usepackage{listings}

@@

\begin{abstract}

    The Python language is highly dynamic, most notably due to late binding. As
    a consequence, program run using Python typically run an order of magnitude
    slower than their C counterpart. It is also a high level languages whose
    semantic can be made more static without much change from a user point of
    view in the case of mathematical applications. In that case, the language
    provides several vectorization opportunities that are studied in this
    paper, and evaluated in the context of Pythran, an ahead-of-time compiler
    that turns Python module into C++ meta-programs.

\end{abstract}

@@

The Python language has grown in audience for the past ten years, even reaching
the world of scientific computations thanks to the \texttt{numpy} module, a
module that provides a MATLAB-like API. As a consequence, more and more code is
being written either in pure Python, generally to prototype an application, or
as a Python and native code mix when performance matters. However, Python
trades performance for dynamicity and does not particularly shines in terms of
performance.

For instance, the natural solution to Project Euler sixth problem ``Find the
difference between the sum of the squares of the first one hundred natural
numbers and the square of the sum`` can be coded as in
Listing~\ref{lst:euler06-py} in Python and as in Listing~\ref{lst:euler06-c} in
C.

\begin{lstlisting}[language=python, label={lst:euler06-py}, caption={Solution to the Project Euler Sixth Problem in Python}]
def solve();
  r = xrange(1, 101)
  a = sum(r)
  return a * a - sum(i*i for i in r)
\end{lstlisting}

\begin{lstlisting}[language=c, label={lst:euler06-c}, caption={Solution to the Project Euler Sixth Problem in C}]
size_t solve() {
  size_t a = 0, s = 0;
  for(size_t i = 0; i< 101; ++i) {
    a += i;
    s += i*i;
  }
  return a * a - s
}
\end{lstlisting}
